\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.75in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]




% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[6]{ % Modified to take 6 arguments
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      #5 \\ % Additional line without italics
      #6 \\ % Additional line without italics
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \color{gray}
  \item
  
\end{flushright}

\vspace{-5pt}

\begin{center}
    \textbf{\Huge \scshape Dennis Mwendwa} \\ \vspace{8pt}
    \small 
    \faIcon{github}
    \href{https://github.com/deninjo?tab=repositories}{\underline{github.com/deninjo}} $  $
    \faIcon{phone-alt}
    {\underline{0700362004}} $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/dennis-mwendwa/}{\underline{linkedin.com/in/dennis-mwendwa}} $  $
    \faIcon{envelope}
    \href{mailto:imwendwadennis@gmail.com}
    {\underline{imwendwadennis@gmail.com}}
\end{center}

% -------------------- PROFESSIONAL SUMMARY --------------------
\section{Professional summary}
Innovative and zealous programmer seeking to leverage extensive background in data analysis and trends. Proficient in Python programming, I have successfully developed and maintained scalable and efficient software applications. Demonstrated strong problem-solving skills by implementing optimized algorithms and data structures in Python, significantly improving system performance. All in all, I am a one that is conversant with new and emerging technologies that tend to benefit me in the various endeavours that I undertake within the tech space with a current peak interest in back-end development.


% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Primary School Education}{January 2006 - June 2016}
      {Kenya Certificate of Primary Education(K.C.P.E)}{GPA: 404/500}
      {Whitestar Academy, Nairobi, Kenya}
    \newline  
       
    \resumeSubheading
      {Secondary School Education}{January 2017 - April 2021}
      {Kenya Certificate of Secondary Education(K.C.S.E)}{GPA: A-}
      {Nairobi School, Nairobi, Kenya}
    \newline

    \resumeSubheading
      {Undergraduate Education}{September 2021 - Current}
      {B.Sc. Computer Science}
      {}
      {Jomo Kenyatta University of Agriculture and Technology}
      {}


  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: C, Python, SQL, PhP, HTML/CSS, \LaTeX} \\
     
     \textbf{Tools}{: Git/GitHub, Unix Shell, VS Code, MySQL Workbench, PyCharm, IBM Cognos, Excel, Power BI, Ms Office, Microsoft Dynamics 365} \\
     \textbf{Operating Systems}{: Linux, Windows} \\
     
    }}
 \end{itemize}

% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart   
    
    
    
    
\resumeProjectHeading
        {\textbf{Analyzed the Relationship Between HIV Prevalence and Multidimensional Poverty} $|$ 
\footnotesize\emph{Python, Pandas, GeoPandas} \\
\footnotesize\emph{Seaborn, Matplotlib, Jupyter}}{}
        
        \resumeItemListStart
        
            \resumeItem{Conducted a cross-national analysis of the relationship between HIV prevalence and multidimensional poverty using datasets from the WHO Global Health Observatory and World Bank}
            
            \resumeItem{Cleaned and preprocessed multi-source datasets; to enable accurate merging and comparison.}
            
            \resumeItem{Integrated HIV and poverty datasets by country and year, forming a comprehensive panel dataset to support temporal and spatial analysis.}
            
            \resumeItem{Built and interpreted correlation matrices to explore statistical relationships between HIV prevalence and poverty sub-indicators (e.g., education, sanitation, electricity)}
            
            \resumeItem{Visualized key trends using time-series plots and scatter plots to support pattern discovery and hypothesis testing using interactive visualization libraries (e.g., Plotly) to enhance data exploration and stakeholder presentation quality.}
            
            \resumeItem{Isolated countries accounting for 75\% of the global HIV burden, which included South Africa, Nigeria, Mozambique, India, and Kenya}

            
            \resumeItem{Analyzed under-five and neonatal mortality in East African Community (EAC) countries using UN IGME data.}
            
            \resumeItem{Filtered the mortality dataset for 8 EAC countries then used GADM shapefiles to visualize latest estimates of under-five and neonatal mortality for these countries via choropleth maps, reinforcing geographic storytelling}
            
         
            
            \resumeItem{Demonstrated ability to work with real-world, imperfect data and draw actionable insights from public health and socio-economic datasets.} 
                     
          \resumeItemListEnd
            
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
    
        \resumeProjectHeading
        {\textbf{Analyzed Kenya Data} $|$ \footnotesize\emph{ Jupyter Notebook ,HTML, Git,VS Code}}{}
        \resumeItemListStart
            \resumeItem{Extracted Kenya's 2019 census data from KNBS}
            \resumeItem{Performed comparative and descriptive insights and visualized the Kenya 2019 census data}
            \resumeItem{Cleaned and transformed Kenya's weather data from 1991-2016, providing quality data}
            \resumeItem{Identified correlations and applied statistical methods to find the best fit model for average data across the years}
            \resumeItem{Analyzed Stock Prices from Historical Data (NSE from 2007 - 2012) to understand patterns, predict future movements, and make data-driven investment decisions.}
            \resumeItem{Predicted the closing price of stocks based on key predictors using ML techniques}
            \resumeItem{Analyzed Road accidents data and used classification models to predict how risky a road is prone to traffic accidents}
            
            \resumeItem{Exported the Jupyter Notebook file to HTML to allow interactive visualizations to be seamlessly integrated with the code and analysis}
          \resumeItemListEnd
          
          
        \resumeProjectHeading
        {\textbf{Analyzed Personal Spotify and Apple Music Data} $|$ \footnotesize\emph{ Power BI ,Excel}}{}
        \resumeItemListStart
            \resumeItem{Extracted personal Spotify and Apple Music data}
            \resumeItem{Cleaned and transformed raw data into useful information}
            \resumeItem{Created interactive dashboards providing comparative and descriptive insights}
            \resumeItem{These dashboards were designed to be dynamic, offering tailored insights at a glance, demonstrating proficiency in Power BI's advanced visualization and data modeling capabilities.}
            \resumeItem{Applied DAX queries to create calculated measures and columns, enabling insights such as most-streamed genres, artists, and time-based listening patterns.}            
          \resumeItemListEnd
        
        

       
 
 
 
 
 
 

 
 

 
        
       
       
       
       
       
       
       
       
       
       
       
       
        
        
        \resumeProjectHeading
{\textbf{Movie Ticket Booking System} $|$ \footnotesize\emph{Python, MySQL, Linux Shell, Power BI, PhP}}{}
\resumeItemListStart
    \resumeItem{Built a robust MySQL database for a ticket booking system, incorporating essential tables for customers, movies, showtimes, theatres, seats, and bookings.}
    \resumeItem{Advanced logic was implemented using triggers to handle tasks like: Dynamic price calculations based on seat category, showtime, and customer type (e.g., applying a 25\% discount for students).}
    \resumeItem{The backend system was developed in Python, leveraging libraries like mysql-connector to connect to the MySQL database. Python scripts acted as the core interface between users and the database.}
    \resumeItem{Python classes (Customer, Movie, Theatre, Seat, etc.) handled operations like: Customer data entry and validation, Displaying movies and their available showtimes, Viewing and managing seating charts, Adding, confirming, and canceling bookings.}
    
    \resumeItem{Distributed the Database via Master-Slave Replication:
        \begin{itemize}
            \item A master-slave replication model was implemented to improve database performance and scalability.
            \item The master database managed all write operations, such as adding bookings, updating customer information, and modifying seat statuses.
            \item The slave databases were optimized for read-heavy operations like retrieving seating charts or displaying available showtimes.
            \item Automated the backup process using cron jobs in combination with database-specific tools (e.g., mysqldump, mysqlbackup).
            \item This architecture enhanced system performance and reduced latency for users by reducing the load on the master node. It also provided redundancy to safeguard against failures.
        \end{itemize}
    }
    
    \resumeItem{A data warehouse was designed and set up to aggregate and store data for analytics.
        \begin{itemize}

            \item ETL pipelines extracted transactional data from the MySQL database, transformed it into meaningful metrics (e.g., total revenue by showtime), and loaded it into the data warehouse.
            \item A star schema was used to optimize the warehouse for analytical queries, with fact tables (e.g., booking data) linked to dimension tables (e.g., customers, movies, showtimes).
            \item The warehouse enabled deeper insights into system operations, such as:
                \begin{itemize}
                    \item Revenue trends and peak booking times.
                    \item Customer behavior analysis (e.g., preferences for certain movies or showtimes).
                    \item Utilization rates of seat categories.
                \end{itemize}
        \end{itemize}
    }
    
 
\pagebreak    
    
   
	\resumeItem{Power BI Integration:
        \begin{itemize}
            \item Connected Power BI to MySQL: Installed the MySQL ODBC driver (9.1). Successfully connected Power BI to your MySQL database using the ODBC connector.
            \item Power BI was used for reporting and visualization, connected either directly to the MySQL database or the data warehouse:
                \begin{itemize}
                    \item Dashboards were created to display real-time insights like popular movies, peak booking periods, seat occupancy rates, and revenue breakdowns.
                    \item Dynamic, user-friendly reports empowered stakeholders to make data-driven decisions.
                \end{itemize}
        \end{itemize}
    }    
    
    
\resumeItem{Currently building the web application implementation}    
    
\resumeItemListEnd
        
        
        
        
        
        
         \resumeProjectHeading
        {\textbf{Chama App} $|$ \footnotesize\emph{Python, C, XAML, .NET Framework, APIs (Google), Git,VS Code}}{}
        \resumeItemListStart
            \resumeItem{Collaboration project for a sacco management system}
            \resumeItem{Developed python SMTP scripts that enable email automation increasing efficiency and time saved}
            \resumeItem{Learned how to connect to gmail servers and use databases in conjunction with Google APIs}
            \resumeItem{Generated reports - individual member and sacco reports}
          \resumeItemListEnd
           
     
          
    \resumeSubHeadingListEnd
    \vspace{-8pt}
     

    
% -------------------- CERTIFICATIONS --------------------

\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Microsoft Certified: Azure Fundamentals:}{		Microsoft} \\
     \textbf{Introduction to Data Analytics:}{Coursera} \\
     \textbf{Data Analysis with Python:}{ Freecodecamp} \\
	\textbf{SQL Intermediate:}{	HackerRank} \\     
     \textbf{Excel for Data Analysis:}{	IBM} \\
     \textbf{Data Visualization and Dashboards with Excel and Cognos:}{	IBM} \\
     \textbf{Alteryx Foundational Micro-Credential:}{		Alteryx} \\
     \textbf{International Computer Drivers License - Level One (ICDL):}{		ICDL Africa} \\
     
 
     
    }}
 \end{itemize}
 

 
 


% -------------------- HOBBIES --------------------

 

\end{document}
